---
title: "grp1_project_package-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{project_package-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, message = FALSE, echo = FALSE, error = FALSE}
library(grp1ProjectPackage)
```

# Introduction to grp1ProjectPackage

The goal of grp1ProjectPackage is to provide functions for data preprocessing for exploratory data analyses. The grp1ProjectPackage simplifies the following tasks.:

-   Loading data from a URL
-   Removing certain columns from a data set
-   Creating a ggplot boxplot
-   Splitting data into training and testing sets

This document introduces all of the tools mentioned above as well as examples of how to apply them to data frames and use them in different real-world scenarios.

## 1. Load data from a URL using `load_data()`

Data is often stored through URLs on the internet.

The following shows an example of using the `load_data()` function using a URL. A garments factory data set is loaded from the URL with 1197 rows and 15 columns. For details on how to use the function, check out `help(load_data)`.

```{r load_data, warning = FALSE, error = FALSE, echo = FALSE}
init_data<-load_data("https://7e6cd356-86ad-4874-abc7-3a69bbbc39e6.filesusr.com/ugd/c5a545_c1b17c070c984dfcb14cf1c3bb0b6e67.csv?dn=garments_worker_productivity.csv")
head(init_data)
```

## Data: `mtcars`

To demonstate the rest of the package, we will use a simplier data set called `mtcars`. This data set has 11 columns, 32 rows and is documented in `?mtcars`. Note that `mtcars` is a data frame and below is the first 6 rows.

```{r dataset, warning=FALSE, echo = FALSE}
head(mtcars)
data <- mtcars
```


# Demonstration of basic functions in grp1ProjectPackage

## 2. Dropping columns with `clean_data()`

Frequently, when dealing with extensive data sets, there may be columns that are unnecessary or unappealing. In that case, you can use the function `clean_data()` to drop those columns. For details on how to use the function, check out `help(clean_data)`.

-   **dropping a single column `qsec` from mtcars**

```{r data_cleaning1, warning = FALSE, error = FALSE}
head(clean_data(data, "qsec"))
```

As you can see above, the column qsec has been dropped from the data frame.

-   **dropping multiple columns from mtcars**

```{r data_cleaning2, warning = FALSE, error = FALSE}
head(clean_data(data, c("mpg","disp","qsec")))
```

Columns `mpg`, `disp`, and `qsec` have been dropped.

-   **When an inappropriate column name is inputted, an error will occur.**

For instance, if the wrong column name mpf is inputted instead of `mpg`. The function will produce an error.

`clean_data(data, "mpf")` will produce the following message: *"Error in clean_data(data, "mpf") : column names incorrect. Please try again"*


## 3. Creating a boxplot using `create_boxplot()`

It is often necessary to have visual representations in order to comprehend data more effectively. Visually displaying data helps to simplify complex problems by transforming data into a more understandable format and showing trends and outliers. A high-quality visualization tells a narrative by eliminating extraneous details and highlighting the crucial informatation.

The following function creates a boxplot from the data given.

For details on how to use the function, check out `help(create_boxplot)`.

```{r plot, warning = FALSE, echo = FALSE,  fig.width = 7, fig.height = 4}
create_boxplot(mtcars, as.factor(data$cyl), mtcars$mpg, "MPG by No. Cylinders", "No. Cylinders", "mpg")
```
A boxplot has been created displaying the MPG by Number of Cylinders.

## 4. Splitting data into training and testing sets using `train_test_split()`
For many model selection techniques splitting the data into training and testing sets is required.

The following function splits the data into training and testing sets based on the given inputs. 

For details on how to use the function, check out `help(create_boxplot)`.
```{r recipe-scale-center, warning = FALSE, error = FALSE}
 train_test_split(mtcars, 0.75, "mpg")
```

The data set has been randomly split into a training set with 75% of the entries and a testing set with 25% of the data.
